---
title: "¡Välkommen y bom dia monde!"
author: "Michael France Nelson"
date: "August 21, 2020"
output:
  prettydoc::html_pretty:
    theme: architect
    highlight: github
    css: !expr here::here("data", "styles.css")
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r build_page, echo = FALSE, eval = FALSE}
require(rmd.utils)
out_dir = here::here("docs")

rmarkdown::render(
  input = rmd.utils::find_file("index.Rmd"),
  output_dir = here::here("docs")
)
```


# This page is under heavy construction!

For now, please follow the links below to view projects, courses, and other resources that I'm involved with.

## Courses

The following are courses that I teach at the University of Massachusetts, Amherst in the Department of Environmental Conservation.

- [Analysis of Environmental Data](/eco_602_634_2020/)

- [Introduction to Quantitative Ecology](/intro_quant_ecol/)

- [Introduction to Geographic Information Systems](/intro_gis/)


## Other UMass links

- [Quantitative Sciences Group](/umass_qsg/)

- [Department of Environmental Conservation at the University of Massachusetts, Amherst](https://eco.umass.edu/)

- [My faculty page at UMass](https://eco.umass.edu/people/faculty/nelson-michael/)


## Course Data

- [Introduction to GIS](/intro_gis/)


# Coding Demos

Here is a collection of short demos of how to perform some common tasks in R:

- [Saving a figure to a file in R/RStudio](r_demos/save_figures_demo.html)
